\textbf{Are regime changes always bad economics? Evidence from daily financial data}

### 2019-06-03 doc/paper.tex
Minor updates to conclusion

\section{Discussion and Conclusion}
Max Weber (\citeyear{weber1947theory}) developed the concept of ``charismatic leadership'' whereby a leader's authority stems from their charisma. Such rule is often found in autocracies with weak institutions and few constraints placed on the power of leaders. \citet{jones2005leaders} show that leaders can have particularly large impacts on economic growth in these settings. It is therefore not surprising that there is often a strong temptation to overthrow ``bad" leaders, even by undemocratic means.

@@

In total, the evidence consequently suggests that abnormal returns tend to be positive following resignations because the regime change likely replaced ``bad'' leaders, and coups can result in positive returns in settings where socialist governments are replaced with more pro-business ones. Conversely, autocratic coups may increase fear of capital appropriation or the implementation of poor economic policies, while assassinations may be merely regarded as highly uncertain events.

>>>>

\section{Discussion and Conclusion}

Markets are said to dislike political instability. We show that this is not necessarily the case, as changes in ruler can give markets a boost when a new regime is expected to offer a more pro-business environment than the previous one.

@@

Taken together, the evidence suggests that abnormal returns tend to be positive following resignations because the regime change likely replaced ``bad'' leaders, and coups can result in positive returns in settings where socialist governments are replaced with more pro-business ones. Conversely, autocratic coups may increase fear of capital appropriation or the implementation of poor economic policies, while assassinations may be merely regarded as highly uncertain events.
